\appendix

\chapter{Hardware}

\section{Installation}

To install the VT132 in an RC2014 or a compatible system, place it in a standard or extended bus socket.

If your backplane does not offer an extended bus, the modem cannot be used via bus pins, instead the modem 6 pin header has to be used.
The extended bus pins are not used for other purposes.

\textbf{On a new VT132, the NVR (Non-volatile RAM) is not initialized.}

At power-on or reset, following the \textbf{Wait} message, a new VT132 will display \textbf{Error} along with a series of bells.
This is expected because the NVR has not been initialized.
Once you write settings to the NVR, this error should not persist.

\section{Jumper settings and headers}
\label{jumperheaders}

The board features the following jumpers:

\begin{tabular}{p{7em} | p{0.71\textwidth}}
\hline
\textbf{Jumper} & \textbf{Function} \\
\hline
JP1 RxA & \multirow{2}{*}{Connect terminal to port A on bus pins} \\
JP2 TxA \\
\hline
JP3 RxB & \multirow{2}{*}{Connect modem to port B on ext. bus pins} \\
JP4 RxB \\
\hline
JP5 Pwr FTDI & Connect Power to FTDI +5V pin \\
\hline
JP6 Pwr Modem & Connect Power to modem header +5V pin \\
\hline
\end{tabular}

Enabling JP1 and JP2 is highly advised, as the VT100 terminal serial connection is not available on a 6 pin header.

If you want to provide power to, or take power from either of the 6 pin headers then JP5 and JP6 will provide power
or isolate the \texttt{Vcc} pin in the \texttt{FTDI Program} and \texttt{Modem Port B} 6 pin headers respectively.

\textbf{Warning:} You should normally only connect one power source to the system at a time.

\begin{tabular}{ c | p{0.38\textwidth} || c | p{0.37\textwidth}}
\hline
\multicolumn{2}{ l || }{FTDI Program} & \multicolumn{2}{ l }{Modem Port B} \\
\hline
\textbf{Pin} & \textbf{Function} & \textbf{Pin} & \textbf{Function} \\
\hline
1 & GND             & 1 & GND \\
2 & not connected   & 2 & CTS \\
3 & Vcc (+5V)       & 3 & Vcc (+5V) \\
4 & Tx              & 4 & Tx \\
5 & Rx              & 5 & Rx \\
6 & not connected   & 6 & RTS \\
\hline
\end{tabular}

If your RC2014 serial module uses the RTS/CTS pins, you can disable JP3+4 and use jumper wires to connect the \textbf{Modem Port B} of the VT132 to your serial module,
as no bus pins are assigned to RTS/CTS.

The \textbf{FTDI Program} header outputs debug messages from the ESP32 microcontroller. You can connect another terminal (or a PC) to watch the debug output.
The output uses 115200 baud, 8 data bits, no parity, 1 stop bit (8-N-1).

It is also possible to flash the ESP32 via this header. To enable the \textit{programming mode}, press and hold \textbf{Reset}, press and hold \textbf{Prog}, release \textbf{Reset}
and release \textbf{Reset}. Another firmware can now be uploaded, eg. via \texttt{esptool}.

\newpage
\section{Buttons}

The VT132 module offers two buttons:

\begin{itemize}[leftmargin=1em]
 \item Reset
 \item Prog
\end{itemize}

The hardware \textbf{Reset} button on the PCB reboots the ESP32 (EN line reset). This will cause both the VT100 terminal and the modem to reset.
Any unsaved settings (terminal and/or modem settings) will be lost.

\textit{Note:} The computer connected to the VT132 will not be reset, so after the reset, you will be in the same program as before.

The hardware \textbf{Prog} button is used to switch the baud rate of the modem. After each press of this button, the modem outputs its new
baud rate to the serial port - so you can press this button repeatedly until you can read your baud rate.

